An Experimental Evaluation of Hybrid Querying on Vectors (EA\&B)

### 2025-07-24 Revision/response.tex

\textbf{Regarding quantization time in index build:}

Of all the evaluated algorithms, only Faiss supports quantization. However, in our experiments, we used the IVF index structure of Faiss without employing quantization. Therefore, no quantization time was included in the reported index build times.

\textbf{Regarding Figure 7 and the exclusion of Vamana:}

We appreciate the observation of reviewer. Figure 7 presents experiments on multi-attribute construction and search, using Boolean AND logic. The Vamana-based methods (FilteredVamana and StitchedVamana) only support Boolean OR logic for multi-attribute search, which is why they were not included. Since other algorithms also do not support multi-attribute queries, we will explain this situation collectively in the corresponding section of the paper to save space.

Please see the section 4.2.2 on Multi-Attribute Construction and Multi-Attribute Query.

\textcolor{blue}{"In this experiment, we only evaluate the algorithms that support this query scenario."}

### 2025-07-24 VLDB2026/main.tex
1

	\textit{\textbf{Multi-Attribute Building and Multi-Attribute Query.}}  
	Compared to single-attribute filtering, multi-attribute joint filtering better reflects real-world scenarios. To evaluate algorithm performance under this setting, we construct the index using 3 uniformly distributed attributes and apply filtering on all 3 attributes simultaneously during queries. \textcolor{orange}{Note that FilterDiskANN only supports Boolean OR logic and does not support Boolean AND. Therefore, its two Vamana-based methods are excluded from the multi-attribute construction and search experiments.}
	%	\textcolor{red}{As Filtered-DiskANN does not support the AND rule used in our multi-attribute queries, it is excluded.}
	%	Compared to single-attribute filtering, multi-attribute joint filtering better reflects real-world application scenarios. To evaluate algorithm performance under such scenario, we construct the index using 3 uniformly distributed attributes and apply filtering conditions on all 3 attributes simultaneously during the query process.

@@

\begin{table*}[htbp]
	\caption{Algorithm Recommendation}
	\resizebox{\textwidth}{!}{
		\begin{tabular}{|l|*{16}{c|}}
			\hline
			\multirow{2}{*}{\textbf{Application Scenarios / Algorithms}} 
			& \multicolumn{6}{c|}{\textbf{AF}} 
			& \multicolumn{5}{c|}{\textbf{RF}} 
			& \multicolumn{5}{c|}{\textbf{AF / RF}} \\
			\cline{2-17}
			& \textbf{NHQ} & \textbf{Filtered} & \textbf{Stitched} & \textbf{CAPS}  & \textbf{UNG} & \textbf{Puck} 
			& \textbf{DSG} & \textbf{iRange} & \textbf{SeRF} & \textbf{UNIFY} & \textbf{Win} 
			& \textbf{ACORN}& \textbf{Faiss} & \textbf{Milvus} & \textbf{VBASE} & \textbf{PASE} \\
			\hline
			\textbf{Query Performance} & H & M & H & M &\textbf{ H} & H & M & M & L & M & H & M/M & M/M & M/M & L/L & L/L \\
			\textbf{Index Time} &M  &M  &M  &M  &M  &H  &L  &M  &H  &L  &L  &L/L &\textbf{H}/ \textbf{H} &M/H  &M/M  &L/L  \\
			\textbf{Peak Memory} &L  &M  &M  &M  &M  &H  &L  &L  &M  &L  &L  &L/L  &\textbf{H}/\textbf{H}  &M/M  &H/M  &H/H \\

			\textbf{Large-Scale Dataset} & H & H & L & L &\textbf{H } &H  &M  &H  &M  &H  &\textbf{H}  &M/L  &L/M  &L/L  &M/M  &-  \\
			\textbf{Rare Attribute \& Low Range} &M  &M  &H  &H &\textbf{H}  &H  &H  &H  &L  &M  &\textbf{H} &M/M  &M/M  &L/L  &L/L  &L/L  \\
			\textbf{Robust to MultiModal Dataset} &H  &H  &L  &H  &H  &L  &M  &H  &M  &H  &H  &H/H  &M/M  &L/L  &L/L  &-/-  \\
			\textbf{Robust to Attribute Distribution} &L  &L  &H  &H  &H  &H  &-  &-  &-  &-  &-  &H/-  &L/-  &H/-  &L/-  &L/-  \\
			\textbf{High LID Dataset} &H  &M  &H  &M  &H  &M  &M  &H  &M  &H  &H  &L/L  &M/H  &L/L  &L/M  &L/L  \\
			\textbf{General-Purpose} &\faCheck  &\faCheck  &\faTimes  &\faTimes  &\faCheck  &\faTimes  &\faTimes  &\faCheck &\faTimes  & \faTimes &\faCheck&\faTimes  &\faCheck  &\faCheck  &\faTimes &\faTimes  \\
			\hline
		\end{tabular}
	}
	\centering
\end{table*}

>>>>

	\textit{\textbf{Multi-Attribute Building and Multi-Attribute Query.}}  
	Compared to single-attribute filtering, multi-attribute joint filtering better reflects real-world scenarios. To evaluate algorithm performance under this setting, we construct the index using 3 uniformly distributed attributes and apply filtering on all 3 attributes simultaneously during queries. \textcolor{orange}{In this experiment, we only evaluate the algorithms that support this query scenario.}
	%	\textcolor{red}{As Filtered-DiskANN does not support the AND rule used in our multi-attribute queries, it is excluded.}
	%	Compared to single-attribute filtering, multi-attribute joint filtering better reflects real-world application scenarios. To evaluate algorithm performance under such scenario, we construct the index using 3 uniformly distributed attributes and apply filtering conditions on all 3 attributes simultaneously during the query process.

@@

\begin{table*}[htbp]
	\caption{Algorithm Recommendation}
	\resizebox{\textwidth}{!}{
		\begin{tabular}{|l|*{16}{c|}}
			\hline
			\multirow{2}{*}{\textbf{Application Scenarios / Algorithms}} 
			& \multicolumn{6}{c|}{\textbf{AF}} 
			& \multicolumn{5}{c|}{\textbf{RF}} 
			& \multicolumn{5}{c|}{\textbf{AF / RF}} \\
			\cline{2-17}
			& \textbf{NHQ} & \textbf{Filtered} & \textbf{Stitched} & \textbf{CAPS}  & \textbf{UNG} & \textbf{Puck} 
			& \textbf{DSG} & \textbf{iRange} & \textbf{SeRF} & \textbf{UNIFY} & \textbf{Win} 
			& \textbf{ACORN}& \textbf{Faiss} & \textbf{Milvus} & \textbf{VBASE} & \textbf{PASE} \\
			\hline
			\textbf{Query Performance} & H & M & H & M &\textbf{H} & H & M & M & L & M & H & M/M & M/M & M/M & L/L & L/L \\
			\textbf{Index Time} &M  &M  &M  &M  &M  &H  &L  &M  &H  &L  &L  &L/L &\textbf{H}/ \textbf{H} &M/H  &M/M  &L/L  \\
			\textbf{Peak Memory} &L  &M  &M  &M  &M  &H  &L  &L  &M  &L  &L  &L/L  &\textbf{H}/\textbf{H}  &M/M  &H/M  &H/H \\

			\textbf{Large-Scale Dataset} & H & H & L & L &\textbf{H} &H  &M  &H  &M  &H  &\textbf{H}  &M/L  &L/M  &L/L  &M/M  &-  \\
			\textbf{Rare Attribute \& Low Range} &M  &M  &H  &H &\textbf{H}  &H  &H  &H  &L  &M  &\textbf{H} &M/M  &M/M  &L/L  &L/L  &L/L  \\
			\textbf{Robust to MultiModal Dataset} &H  &H  &L  &H  &\textbf{H}  &L  &M  &H  &M  &H  &\textbf{H}  &H/H  &M/M  &L/L  &L/L  &-/-  \\
			\textbf{Robust to Attribute Distribution} &L  &L  &H  &H  &H  &H  &-  &-  &-  &-  &-  &H/-  &L/-  &\textbf{H}/-  &L/-  &L/-  \\
			\textbf{High LID Dataset} &H  &M  &H  &M  &\textbf{H}  &M  &M  &H  &M  &H  &\textbf{H}  &L/L  &M/H  &L/L  &L/M  &L/L  \\
			\textbf{General-Purpose} &\faCheck  &\faCheck  &\faTimes  &\faTimes  &\faCheck  &\faTimes  &\faTimes  &\faCheck &\faTimes  & \faTimes &\faCheck&\faTimes  &\faCheck  &\faCheck  &\faTimes &\faTimes  \\
			\hline
		\end{tabular}
	}
	\centering
\end{table*}
